Baseline centering problem

### 2018-12-13 paper/tangotd.tex

The left Bellman equation on $\Delta^{-1}$ is equivalent to
simultaneously solving the Bellman equation with all possible reward
functions, generated by $\1_{s'}$ for all possible target states $s'$.

@@

If the state space is finite, an exact
solution is indeed $E=\R^{\#S}$ with a one-hot representation for $f$,
and the true matrix $\Delta^{-1}$ for $\green$, namely,
\begin{equation}
f(s_2)=\1_{s_2}/\rho(s_2),\qquad
(\green(s_1))_{s_2}=(\Delta^{-1})_{s_1s_2}
\end{equation}
or equivalently, $f(s_2)=\1_{s_2}$ and
$(\green(s_1))_{s_2}=(\Delta^{-1})_{s_1s_2}/\rho(s_2)$. \footnote{The solution to
such representation problems is never unique because $E$ is an arbitrary
space and one may always make a change of basis in $E$, e.g., dividing
the $s_2$-coordinate by $\rho(s_2)$.}
But with infinite or continuous state spaces, we have to find a more
compact representation.

>>>>

More precisely, $\Delta^{-1}_{ss'}$ is the number of paths from $s$ to
$s'$ weighted by their probabilities. When observing a transition $s_1\to
s_2$, the left equation updates paths from $s_1$; the right equation
updates paths to $s_2$. I believe both are important. The right equation
does not exist when working with a single ``target'' reward function $R$.

The left Bellman equation on $\Delta^{-1}$ is equivalent to
simultaneously solving the Bellman equation with all possible reward
functions, generated by $\1_{s'}$ for all possible target states $s'$.
Using only the left Bellman equation treats all targets $s'$ as
completely independent problems for learning.

@@

If the state space is finite, an exact
solution is indeed $E=\R^{\#S}$ with a one-hot representation for $f$,
and the true matrix $\Delta^{-1}$ for $\green$, namely,
\begin{equation}
f(s_2)=\1_{s_2}/\rho(s_2),\qquad
(\green(s_1))_{s_2}=(\Delta^{-1})_{s_1s_2}
\end{equation}
or equivalently, $f(s_2)=\1_{s_2}$ and
$(\green(s_1))_{s_2}=(\Delta^{-1})_{s_1s_2}/\rho(s_2)$. \footnote{The solution to
such representation problems is never unique because $E$ is an arbitrary
space and one may always make a change of basis in $E$. More precisely,
if $B$ is any invertible linear map on $E$, then changing $f\gets Bf$,
$\green\gets (\transp{B})^{-1}\green$ produces a new solution; indeed
this preserves $\green\cdot f$. This may
be useful to ``renormalize'' once in a while, eg setting $f$ to have
unit covariance, which may help with numerical conditioning.} 
But with infinite or continuous state spaces, we have to find a more
compact representation.
